---
title: "Exercise 5"
author: "Put your name here"
date: "Put the date here"
output: html_document
---

# Task 1: Reflection

Put your reflection here


# Task 2: Essential pandemic construction

The New York City Department of Buildings (DOB) maintains [a list of construction sites](https://www1.nyc.gov/assets/buildings/html/essential-active-construction.html) that have been categorized as "essential" during the city's shelter-in-place pandemic order.

## Load and clean data

First we load and clean the data.

```{r load-clean-data, warning=FALSE, message=FALSE}
# You'll only need the tidyverse library for this exercise
library(tidyverse)
theme_set(theme_linedraw())

# Load original data
essential_raw <- read_csv("data/EssentialConstruction.csv")

# Clean the data a little
# Some of the borough names are in ALL CAPS, so we use str_to_title() to convert
# everything in the column to title case.
# We also make BOROUGH and CATEGORY factors (or categorical variables)
essential <- essential_raw %>% 
  mutate(BOROUGH = str_to_title(BOROUGH),
         BOROUGH = factor(BOROUGH),
         CATEGORY = factor(CATEGORY))
```

## Approved projects by borough

Right now there's a row for each approved construction site. We need to condense that down to get counts of construction sites by different variables. We can do this by using `group_by()` and `summarize()`

```{r summarize-data-borough}
essential_by_borough <- essential %>% 
  group_by(BOROUGH) %>% 
  summarize(total = n()) %>% 
  mutate(proportion = total / sum(total))
```

```{r plot-borough-summary}
ggplot(essential_by_borough, aes(x = reorder(BOROUGH, desc(proportion)),
                                 y = proportion, 
                                 fill = BOROUGH)) +
  geom_col() +
  scale_fill_viridis_d(option = "magma", end = 0.8) +
  scale_y_continuous(labels = scales::percent) +
  guides(fill=FALSE) +
  labs(
    x = "Borough",
    y = "Proportion"
  )
```


## Approved projects by category

```{r summarize-data-category}
# Create a summarized dataset of projects by category
#
# I won't give you the code for this (big hint though: copy the code for the
# borough summary and change just one thing)
essential_by_category <- essential %>% 
  group_by(CATEGORY) %>% 
  summarize(total = n()) %>% 
  mutate(proportion = total / sum(total))
```

```{r plot-category-summary}
# Add a lollipop chart here
ggplot(essential_by_category, aes(x = reorder(CATEGORY, proportion), 
                                  y = proportion, 
                                  color = CATEGORY)) +
  geom_pointrange(aes(ymin = 0, ymax = proportion), size = 1.5, fatten = 1.5) +
  scale_color_viridis_d() +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  guides(color=FALSE) +
  labs(
    x = "Category",
    y = "Proportion"
  )
```


## Approved projects across borough and category

```{r summarize-data-heatmap}
# Create a summarized dataset of projects by both borough and category
#
# I also won't give you the code to make the summary for the heatmap. You'll
# need to group by two variables to make the summary. IMPORTANTLY you'll also
# need to add another group_by() in between summarize() and mutate(), otherwise,
# R will calculate percentages in unexpected groups. 
#
# If you want the percentages of categories to add up to 100% in each borough,
# you'll want to group by borough before calculating the proportion; if you want
# the percentages of boroughs to add up to 100% in each category, you'll want to
# group by category
```

```{r plot-heatmap}
# Add a heatmap here with geom_tile()
essential %>% 
  group_by(BOROUGH, CATEGORY) %>% 
  summarize(total = n()) %>%
  group_by(CATEGORY) %>% 
  mutate(proportion = total / sum(total)) %>% 
  ggplot(aes(reorder(BOROUGH, proportion), CATEGORY, fill = proportion)) +
    geom_tile() +
    theme_classic() +
    scale_fill_viridis_c(option = 'inferno', labels = scales::percent) + 
    theme(legend.position='bottom', legend.text = element_text(angle = 90, hjust = 1)) +
    guides(fill = guide_colourbar(title = "Proportion", 
                                  title.vjust = 0.8,
                                  frame.colour = 'black')) +
    labs(
      x = "Borough",
      y = "Category"
    )
```
