---
title: "Exercise 5"
author: "Put your name here"
date: "Put the date here"
output: html_document
---

# Task 1: Reflection

* If your document layout uses caption blocks underneath each figure, then place the figure titles as the first element of each caption block, not on top of the figures;

* Short descriptive assertions for titles and subtitles;

* Some key rules for table layout are the following:

    1. Do not use vertical lines.
    2. Do not use horizontal lines between data rows. (Horizontal lines as separator between the title row and the first data row or as frame for the entire table are fine.)
    3. Text columns should be left aligned.
    4. Number columns should be right aligned and should use the same number of decimal digits throughout.
    5. Columns containing single characters are centered.
    6. The header fields are aligned with their data, i.e., the heading for a text column will be left aligned and the heading for a number column will be right aligned.
    
* Grid lines show only be used in cases where they assist the perception of elements on the graph, but always should be used carefully and in a subtle way.

# Task 2: Ugly plot

Duncan Greere has collected a database of 48 Soviet dogs who flew as test subjects in USSR's space program in the 1950s and 60s. [The original data can be found here](https://airtable.com/universe/expG3z2CFykG1dZsp/sovet-space-dogs).

## Load and clean data

First we load and clean the data.

```{r load-clean-data, warning=FALSE, message=FALSE}
# You'll only need the tidyverse library for this exercise
library(tidyverse)

space_dogs_raw <- read_csv("data/Dogs-Database.csv")

space_dogs <- space_dogs_raw %>% 
  # The Fate column seems to either say "Survived" or "Died <DATE>", so we make
  # a new binary version of the Fate column that is "Survived" if the dog
  # survived and "Died" otherwise
  mutate(Fate_binary = ifelse(Fate == "Survived", "Survived", "Died")) %>% 
  # The data lists the dates of each flight, separated by a comma. To convert
  # that to a number, we do a little trick: count the number of commas in the
  # cell and add 1 (if there were 2 flights, there would be 1 comma, etc.)
  mutate(Flights_num = str_count(Flights, ",") + 1)
```

There are actually some interesting trends here! Female dogs were far less likely to die and went on way more flights than their male counterparts, but that's in part because the USSR used almost only male dogs from 1951-1954, so those dogs faced the early prototypes of rockets and capsules.

```{r summarize-data}
# Summarize the data by fate and gender
space_dogs_summarized <- space_dogs %>% 
  group_by(Fate_binary, Gender) %>% 
  summarize(total_dogs = n(),
            total_flights = sum(Flights_num))

space_dogs_summarized
```

## Ugly plot

But the trends don't matter here. What matters is hideous plots. Change the colors, modify the theme, add labels, etc. and make this ugly. You can leave the `geom_pointrange()` as is, or you can mess with it too (or even change it to a bar chart or pie chart or heatmap or something if you feel up to it).

```{r ugly-plot}
# Making it faceted with a free scale to make it even worse to interpret.

ugly_plot <- ggplot(data = space_dogs_summarized, 
                    mapping = aes(x = Gender, y = total_flights, color = Gender)) +
  geom_pointrange(aes(ymin = 0, ymax = total_flights), size = 2, 
                  position = position_dodge(width = 0.5)) +
  facet_wrap(~Fate_binary, scales = 'free') +
  theme_classic() +
  scale_color_viridis_d(option = 'cividis', end = 0.3)

ugly_plot + theme(axis.line = element_line(colour = "bisque2"), 
    axis.ticks = element_line(colour = "gray19", 
        linetype = "dashed"), panel.grid.major = element_line(colour = "aliceblue", 
        linetype = "dotted"), panel.grid.minor = element_line(linetype = "dotdash"), 
    legend.text = element_text(family = "AvantGarde"), 
    legend.title = element_text(family = "AvantGarde"), 
    panel.background = element_rect(fill = "burlywood4", 
        colour = "coral2"), plot.background = element_rect(fill = "darkseagreen4", 
        colour = "blanchedalmond"), strip.background = element_rect(fill = "brown1"), 
    strip.text = element_text(family = "mono"), 
    legend.key = element_rect(fill = "gray89"), 
    legend.background = element_rect(fill = "khaki3"), 
    legend.position = "top", legend.direction = "horizontal")
```

```{r}
# Save the plot as a PNG with ggsave()
ggsave('ugliest_plot.png', plot = ugly_plot)
```
