---
title: "Exercise 6"
author: "Put your name here"
date: "Put the date here"
output: html_document
---

# Task 1: Reflection

* When making a histogram, always explore multiple bin widths.
* Always verify that your density estimate does not predict the existence of nonsensical data values. 
* To visualize several distributions at once, kernel density plots will generally work better than histograms. 

# Task 2: Visualizing uncertainty with gapminder

For this exercise you'll revisit Hans Rosling's gapminder data on health and wealth. Install the **gapminder** package if you haven't already. Also install the **ggridges** and **gghalves** packages.

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)  # For ggplot, dplyr, and friends
library(gapminder)  # For health/wealth data
library(ggridges)   # For ridge plots
library(gghalves)   # For half geoms
theme_set(theme_light())
```

## Histograms

Make a histogram of *logged* GDP per capita for 1997 only, across all five continents. 

```{r filter-gapminder-1997}
# Create a filtered dataset
gapminder_97 <- gapminder %>% 
  filter(year == 1997)
```

```{r plot-histogram}
# Add a histogram here. You'll probably want to fill and facet.
# You'll also need to add scale_x_log10()
ggplot(gapminder_97, aes(x = gdpPercap, fill= continent)) +
  geom_histogram(bins = 10, binwidth = 0.25, boundary = 10) +
  facet_wrap(~ continent) +
  scale_x_log10() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1))
```


## Densities

Make a ridge plot of life expectancy over time, from 1952 to 2007. You'll need to use the full gapminder data, not the 1997-only data.

```{r plot-ridgeplot}
# Add a ridge plot here
ggplot(gapminder, aes(x = lifeExp, y = fct_rev(factor(year)), fill = ..x.., 
                      linetype = ifelse(continent == 'Africa', 'African continent', 'Other continents'))) +
  geom_density_ridges_gradient(quantile_lines = TRUE, quantiles = 2) +
  scale_fill_viridis_c(begin = 0.2) +
  guides(fill = FALSE) +
  theme(legend.title = element_blank()) + 
  labs(
    x = 'Average Life Expectancy', 
    y = ''
  )

ggplot(gapminder, aes(x = lifeExp, y = fct_rev(factor(year)), fill = ..x..)) +
  geom_density_ridges_gradient(quantile_lines = TRUE, quantiles = 2) +
  scale_fill_viridis_c(begin = 0.2) +
  guides(fill = FALSE) +
  labs(
    x = 'Average Life Expectancy', 
    y = ''
  )
```


## Boxes, violins, and friends

Make a filtered dataset that selects data from only 2007 *and* removes Oceania. Show the distribution of *logged* GDP per capita across the *four* continents using some combination of boxplots and/or violin plots and/or strip plots, either overlaid on top of each other, or using their `geom_half_*()` counterparts from **gghalves**.

```{r filter-gapminder-2007-sans-oceania}
# Create a filtered dataset
gm_07_nooc <- gapminder %>%
  filter(year == 2007 & continent != 'Oceania')
```

```{r plot-distribution}
# Add a plot here. You'll want to use either scale_x_log10() or scale_y_log10(),
# depending on which direction your boxplots/violin plots/etc. go
ggplot(gm_07_nooc,
       aes(x = fct_rev(continent), y = gdpPercap)) +
  geom_half_boxplot(aes(fill = continent), alpha = 0.7, side = "l", width = 0.5, nudge = 0.1, outlier.alpha = 0) +
  geom_half_point(aes(color = continent), side = "l", size = 0.5) +
  geom_half_violin(aes(fill = continent), side = "r") +
  scale_y_log10(labels = scales::dollar) +
  guides(color = FALSE, fill = FALSE) + 
  coord_flip() +
  labs(
    title = 'GDP per capita distribution (2007)',
    subtitle = 'Divided by continent',
    y = 'GDP per capita (US$)',
    x = ''
  )
```
