---
title: "Exercise 10"
author: "Put your name here"
date: "Put the date here"
output: html_document
---

# Task 1: Reflection

* Try making descriptive dashboards, that is, with text, so as to not lose important aspects of the data in the dashboard.


# Task 2: Interactive plots

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(plotly)
library(gapminder)

continent_info <- gapminder %>% 
  distinct(country, continent)

savings <- LifeCycleSavings %>% 
  rownames_to_column(var = 'country') %>%  
  left_join(continent_info, by = 'country') %>% 
  filter(!is.na(continent))
```

Do the following:

1. Make a plot. Any kind of plot will do (though it might be easiest to work with `geom_point()`).

2. Make the plot interactive with `ggplotly()`. 

3. Make sure the hovering tooltip is more informative than the default.

Good luck and have fun!

```{r}
set.seed(2020)

p <- savings %>% 
  ggplot(aes(x = sr, y = continent, color = continent)) +
  geom_jitter(aes(text = country), width = 0, height = 0.2, alpha = 0.5) +
  labs(
    x = "Savings ratio",
    y = NULL
  ) +
  guides(
    color = FALSE
  )

ggplotly(p, tooltip = "text")
```

