---
title: "Exercise 11"
author: "Put your name here"
date: "Put the date here"
output: html_document
---

# Task 1: Reflection

* Only truncate the y-axis when:
  * Small changes matter;
  * The scale is distorted;
  * When zero values are impossible.

* Never truncate x-axis for missing data.
* Don't draw lines between points on an x-axis of categorical data, it gives the illusion of a continuous axis,
use lollipop charts instead.


# Task 2: Visualizing time

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
theme_set(theme_bw(base_family = "Roboto"))
# Load data here

huron_levels <- LakeHuron %>% 
  as.numeric() %>%
  as_tibble() %>% 
  mutate(year = c(1875:1972)) %>% 
  as_tsibble(index = year)


```

Do the following:

1. Load some time-related data

2. Make a plot to show how that data changes over time.

3. Explain why you chose to visualize the data the way you did.

```{r first-plot}
real_plot <- ggplot(huron_levels, aes(x = year, y = value)) +
  geom_line(color = '#296e6b') +
  geom_point(color = '#296e6b') +
  labs(
    x = NULL,
    y = "Water level (ft)",
    title = "Lake Huron Water levels",
    subtitle = "Measured in feet, from 1875 to 1975",
    caption = "Arrow indicates the lowest value ever recorded."
  ) +
  theme(plot.title = element_text(face = "bold")) +
  annotate(geom = "segment", x = 1975, xend = 1965, y = 577, yend = 576, color = "#FF851B", arrow = arrow(angle = 15, length = unit(0.5, "lines")))
```

```{r decomposition}
library(feasts)

huron_comps <- huron_levels %>%  
  model(stl = STL(value)) %>% 
  components()

trend_plot <- ggplot(huron_comps, aes(x = year, y = trend)) +
  geom_line(color = '#296e6b', size = 1) +
  labs(
    x = NULL, 
    y = 'Trend (ft)'
  )
```

```{r}
library(patchwork)

real_plot + trend_plot + 
  plot_layout(ncol = 1)
```

