---
title: "Exercise 13"
author: "Put your name here"
date: "Put the date here"
output: html_document
---

# Task 1: Reflection

* Make word counts, not word clouds.



# Task 2: Word frequencies

Download 4+ books by some author on [Project Gutenberg](http://www.gutenberg.org/). Jane Austen, Victor Hugo, Emily Brontë, Lucy Maud Montgomery, Arthur Conan Doyle, Mark Twain, Henry David Thoreau, Fyodor Dostoyevsky, Leo Tolstoy. Anyone. Just make sure it's all from the same author.

Make these two plots and describe what each tell about your author's books:

1. Top 10 most frequent words *in each book*
2. Top 10 most unique words *in each book* (i.e. tf-idf)

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(tidytext)
library(gutenbergr)

theme_set(theme_bw(base_family = "Roboto"))
```

```{r get-data-from-gutenberg}
# Lovecraft: The Dunwich Horror, The Shunned House
# Edgar Allan Poe: Complete works vol 1, vol 2
# Richard Chambers: The King in Yellow
# Arthur Machen: The Great God Pan

horrors <- gutenberg_download(c(50133, 31469, 2147, 2148, 8492, 389), meta_fields = c("title", "author")) %>% 
  filter(text != "")
```

```{r basic-word-counting}

horrors_words <- horrors %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words) %>% 
  filter(!(word %in% c("thou", "thy", "haue", "thee", "thine", "ye", "ha", "ugh")))

horrors_bigrams <- horrors %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>% 
  filter(!word1 %in% c(stop_words$word, "thou", "thy", "haue", "thee", "thine", "ye",
                       "ha", "ugh")) %>%
  filter(!word2 %in% c(stop_words$word, "thou", "thy", "haue", "thee", "thine", "ye",
                       "ha", "ugh")) %>% 
  unite(bigram, word1, word2, sep = " ") %>% 
  mutate(bigram = str_to_title(str_remove_all(bigram, "_")))

bigram_by_title <- horrors_bigrams %>% 
  count(title, bigram, sort = TRUE) %>% 
  # Keep top 15 in each play
  group_by(title) %>% 
  top_n(15) %>% 
  ungroup() %>% 
  # Make the words an ordered factor so they plot in order
  mutate(bigram = reorder_within(bigram, n, title))

bigram_by_author <- horrors_bigrams %>% 
  count(author, bigram, sort = TRUE) %>% 
  # Keep top 15 in each play
  group_by(author) %>% 
  top_n(15) %>% 
  ungroup() %>% 
  # Make the words an ordered factor so they plot in order
  mutate(bigram = reorder_within(bigram, n, author))
```

```{r plot-word-counts}
ggplot(bigram_by_author, aes(y = bigram, x = n, fill = author)) + 
  geom_col() + 
  guides(fill = FALSE) +
  labs(y = "Count", x = NULL, 
       title = "15 most frequent bigrams in classic Horror stories",
       subtitle = "Grouped by author") +
  facet_wrap(vars(author), scales = "free_y") +
  scale_y_reordered() +
  scale_fill_viridis_d(option = 'magma', end = 0.8) +
  theme(plot.title = element_text(face = "bold"))

ggplot(bigram_by_title, aes(y = bigram, x = n, fill = title)) + 
  geom_col() + 
  guides(fill = FALSE) +
  labs(y = "Count", x = NULL, 
       title = "15 most frequent bigrams in classic Horror stories",
       subtitle = "Grouped by work") +
  facet_wrap(vars(title), scales = "free_y") +
  scale_y_reordered() +
  scale_fill_viridis_d(option = 'magma', end = 0.8) +
  theme(plot.title = element_text(face = "bold"))
```

```{r sentiment-analysis}
sentiments <- horrors_words %>% 
  inner_join(get_sentiments("bing"))

sentiments %>% 
  count(author, sentiment) %>% 
  ggplot(aes(x = sentiment, y = n, color = author, shape = sentiment)) +
    geom_pointrange(aes(ymin = 0, ymax = n), size = 1, 
                  position = position_dodge(width = 0.5)) +
    scale_alpha_manual(values = c(0.5, 1)) +
    facet_wrap(vars(author))
```

```{r sentiment-line-split}
sentiments_by_line <- sentiments %>% 
  # Divide lines into groups of 100
  mutate(line = row_number(),
         line_chunk = line %/% 100) %>% 
  # Get a count of postiive and negative words in each 100-line chunk in each play
  count(title, line_chunk, sentiment) %>% 
  # Convert the sentiment column into two columns named "positive" and "negative"
  pivot_wider(names_from = sentiment, values_from = n) %>% 
  # Calculate net sentiment
  mutate(sentiment = positive - negative)

ggplot(sentiments_by_line,
       aes(x = line_chunk, y = sentiment, fill = sentiment)) +
  geom_col() +
  scale_fill_viridis_c(option = "magma", end = 0.9, name = "Sentiment") +
  facet_wrap(vars(title), scales = "free_x") +
  labs(
    title = "Sentiment change in book",
    x = "Line",
    y = "Sentiment"
  ) +
  theme(plot.title = element_text(face = "bold"))
```

